---
output: pdf_document
---
##Retail Performance By BD - Adjusted Hug + Handshake Net BoB
```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## v7 uses the July 2017 Market structure and split markets of North LA and South Shore

## v5 intends to automate the start dates of MTD, QTD, and YTD ranges

## Look at lines 511-515 to update; as quarter changes also update QTD
## Need to export .csv files with every official pull with system time in name
#setwd("D://Users/SPritchard/Downloads")

library(ggplot2)
library(dplyr, quietly = TRUE, verbose = FALSE, warn.conflicts = FALSE)
library(gridExtra, quietly = TRUE, warn.conflicts = FALSE)

new.month <- function(downloads.name) {
  library(xlsx,quietly = TRUE, verbose = FALSE, warn.conflicts = FALSE)
  full.path <- paste0("D://Users/SPritchard/Downloads/",downloads.name)
  month.data <- read.xlsx2(full.path, sheetIndex = 1, colIndex = c(1:39), startRow = 2, 
                          colClasses = c(rep("character", 4), "numeric", rep("character", 2), 
                                         "numeric", rep("character", 6), rep("numeric", 4),  
                                         rep("character", 4), rep("numeric", 6), rep("character", 6), 
                                         "numeric", rep("character", 4)), stringsAsFactors = FALSE)
  message <- paste(downloads.name, "has been read in and dim equal") 
  #print(message)
  #print(dim(month.data))
  month.data

}

#END new.month.R

mtd.prep <- function(mtd.obj, class.data.obj, st.date.priormnth, end.date.curmnth, cache.if.exists = TRUE){
  
  cached.file.name <- paste0("D://Users/SPritchard/Music/Documents/R/cached/netbob.fix.thru", gsub("-", "", end.date.curmnth),".csv")
  if(cache.if.exists == FALSE){
    cached.file.name <- "D://Users/SPritchard/Music/Documents/R/cached/fake.name/"
  }
  
  if(file.exists(cached.file.name)){
    cy.append2 <- read.csv(cached.file.name, stringsAsFactors = FALSE)
  } else{
  
  three.fix <- function(df.to.fix, class.data.object, start.date, end.date){
    
    #READ IN email.glean.R (inside three.fix.R)
    
    email.glean <- function(df.to.fix) {
      df.f <- df.to.fix
      df.len <- nrow(df.f)
      df.col.names <- colnames(df.f)
      if(df.col.names[36] != "EMAIL1"){
        #print("ERROR: Column 36 not EMAIL1 in input")
      }
      split.addr <- strsplit(df.f[,36], "@")
      doms <- character(length = 0)
      for(i in 1:df.len){
        dom.i <- split.addr[[i]][2]
        doms <- c(doms, dom.i)
        
      }
      #print("domains extracted")
      df.wdoms <- cbind(df.f, doms)
      #print(head(df.wdoms, 1))
      
      
      sch.emails <- read.csv("D://Users/SPritchard/Music/Documents/R/net-bob-scripts/emaildoms.schools2.csv", stringsAsFactors = FALSE)
      col.sch.emails <- colnames(sch.emails)
      sch.emails.rows <- nrow(sch.emails)
      all.doms <- sch.emails[,3]
      #print(class(all.doms))
      #print(colnames(sch.emails))
      
      #fixed.enrolls <- vector(mode = "character", length = 39)
      for(t in 1:sch.emails.rows){
        df.f.t <- df.wdoms[df.wdoms$doms %in% all.doms[t],]
        msg.t <- paste0("checking email for row ", t, " of ", sch.emails.rows)
        #print(msg.t)
        
        t.name <- row.names(df.f.t)
        
        if(nrow(df.f.t) >=1) {
          for(q in 1:nrow(df.f.t)){
            if(df.f.t[q,21] == ""){
              df.f.t[q,21] <- sch.emails[t, 4]
            }
          }
          
        } 
        
        if(nrow(df.f.t) >=1) {
          for(q in 1:nrow(df.f.t)){
            df.wdoms[rownames(df.wdoms) == t.name[q],] <- df.f.t[q,]
          }
        }
     
      }
      df.wdoms
    }
    # END OF email.glean.R (inside three.fix.R)
    
    #READ IN priv.venue.fix2.R (inside three.fix.R)
    
    priv.venue.fix2 <- function(df.to.fix, now.class.object, start.date, end.date){
      
      all.netbob <- sum(df.to.fix$NETBOB)
      #print(paste("all net bob equals", all.netbob))
      missing.r1 <- df.to.fix[df.to.fix$SCHOOL.NAME == "",]
      missing.nb1 <- sum(missing.r1[,27])
      #print(paste("all net bob equals", all.netbob))
      #print(paste("missing net bob equals", missing.nb1))
      
      now.class.object[,15] <- as.Date(now.class.object[,15], "%m/%d/%Y")
      sdate <- as.Date(start.date)
      edate <- as.Date(end.date)
      now.class.short <- now.class.object[now.class.object$Enrollment.Date >= sdate & now.class.object$Enrollment.Date <= edate ,]
      
      
      pri.vens <- read.csv("D://USers/SPritchard/Music/Documents/R/net-bob-scripts/private-class-venues.csv", stringsAsFactors = FALSE)
      
      classobj.ids <- now.class.short[now.class.short$Market %in% pri.vens$facility.market 
                                      & now.class.short$Facility %in% pri.vens$facility, ]
      pri.ids.sch <- merge(classobj.ids, pri.vens, by.x = "Facility", by.y = "facility", all.y = FALSE)
      #pri.narrow <- pri.ids[,c(8,10,12,13,14,15)]
      
      #print(head(classobj.ids))
      #print(head(pri.ids.sch))
      
      df.f <- df.to.fix
      df.col.names <- colnames(df.f)
      adjusts <- pri.ids.sch
      adjust.rows <- nrow(adjusts)
      adjusts.ids <- adjusts[,12]
      market.hier <- read.csv("D://Users/SPritchard/Music/Documents/R/net-bob-scripts/market.hierarchy.csv", stringsAsFactors = FALSE)
      #print(head(adjusts.ids))
      fixed.enrolls <- vector(mode = "character", length = 22)
      for(i in 1:adjust.rows){
        df.f.i <- df.f[df.f$ENROLLMENT.ID %in% adjusts.ids[i],]
        
        msg.i <- paste0("Checking EID ", i, " of ", adjust.rows, " in private class venues")
        #print(msg.i)
        
        #print("df.f.i dim equals")
        #print(dim(df.f.i))
        #print(paste("i equals", i))
        i.name <- row.names(df.f.i)
        #print(i.name)
        #print(paste("df.f dim equals", dim(df.f)))
        #print(head(df.f, 2))
        
        if(nrow(df.f.i) >= 1) { df.f.i[,4] <- adjusts[i, 25]} #market
        
        i.hier <- market.hier[market.hier$MARKET_NAME == adjusts[i, 25],]
        #print(adjusts[i, 25])
        #print(i.hier)
        df.f.i[,c(1,2,3)] <- i.hier[,c(1,2,3)] # aligns territory, region & market group with new market
        
        if(nrow(df.f.i) >= 1) { df.f.i[,21] <- adjusts[i, 24]} #school
        #print(df.f.i)
        df.f.i <- df.f.i[1,] #first row only in case of mult entries with EID such as drop switch
        df.f[rownames(df.f) == i.name,] <- df.f.i
        #print(i)
        #print(df.f.i)
      }
      #print(paste("all net bob equals", all.netbob))
      #print(paste("missing net bob equals", missing.nb1))
      
      missing.r2 <- df.f[df.f$SCHOOL.NAME == "",]
      #print(colnames(df.f))
      missing.nb2 <- sum(missing.r2[,27])
      #print(paste("missing net bob after priv.venue.fix2 equals", missing.nb2))
      perc.miss1 <- (missing.nb1/all.netbob)
      perc.miss2 <- (missing.nb2/all.netbob)
      #print(paste0("% of Net Bob missing school in input = ", (round(perc.miss1, 3)*100), "%"))
      
      #print(paste0("% of Net Bob missing school in OUTPUT = ", (round(perc.miss2, 3))*100, "%"))
      #print(paste("Additional Net Bob assigned school name =", round(missing.nb1-missing.nb2)))
      df.f
      
      #print(head(now.class.short))
    }
    
    # END OF READ IN priv.venue.fix2.R (inside three.fix.R)
    
    # READ IN dupe.schools.R (inside three.fix.R)
    
    dupe.schools <- function(df.to.fix){
      dfs <- df.to.fix
      dschools.tbl <- read.csv("D://Users/SPritchard/Music/Documents/R/net-bob-scripts/dupe.schools.csv", stringsAsFactors = FALSE)
      #print("dupe table read in")
      dfs.rows <- nrow(dfs)
      #print(dfs.rows)
      for(p in 1:dfs.rows){
        #print(paste0("Checking for dupes in row ", p, " of ", dfs.rows))
        if(dfs$SCHOOL.NAME[p] %in% dschools.tbl$Duplicate.Name ){
          dupe.row <- dschools.tbl[dschools.tbl$Duplicate.Name == dfs$SCHOOL.NAME[p],]
          if(dfs$CP4.MARKET[p] == dupe.row[1,1]){
            dfs$SCHOOL.NAME[p] <- dupe.row[1,3]  
          }
          
        }
      }
      dfs
    }
    
    # END OF READ IN dupe.schools.R (inside three.fix.R)
    
    # USE FUNCTIONS (inside three.fix.R)
    
    df.gleaned <- email.glean(df.to.fix)
    
    df.priv <- priv.venue.fix2(df.gleaned, class.data.object, start.date, end.date )
    
    df.unduped <- dupe.schools(df.priv)
    
    missing.r1 <- df.to.fix[df.to.fix$SCHOOL.NAME == "",]
    missing.nb1 <- sum(missing.r1$NETBOB, na.rm = TRUE)
    
    missing.r2 <- df.unduped[df.unduped$SCHOOL.NAME == "",]
    missing.nb2 <- sum(missing.r2$NETBOB, na.rm = TRUE)
    all.netbob <- sum(df.to.fix$NETBOB, na.rm = TRUE)
    
    perc.miss1 <- (missing.nb1/all.netbob)
    perc.miss2 <- (missing.nb2/all.netbob)
    #print(paste0("% of Net Bob missing school in input = ", (round(perc.miss1, 3)*100), "%"))
    
    #print(paste0("% of Net Bob missing school in OUTPUT = ", (round(perc.miss2, 3))*100, "%"))
    #print(paste("Additional Net Bob assigned school name =", round(missing.nb1-missing.nb2)))
    
    df.unduped
  }
  # END OF three.fix.R
  
  # Purpose: adds HHW category and whether to include or exclude as a partner school
  # Next step 2: instead of NA schools not on the list or blank should be "Unknown"
  # has an extra row of zeros at top which can be removed
  
  hhpart.append <- function(df.append){
    #1 import filter file
    #2 add hug, handshake, Wave, Unknown, and Exclude, Okay to df.append
    #3 intermediate step of keepiing original doc
    hh.list <- read.csv("D://Users/SPritchard/Music/Documents/R/net-bob-scripts/hh.partners.csv", stringsAsFactors = FALSE)
    df.length <- nrow(df.append)
    df.width <- length(colnames(df.append))
    matrix1 <- matrix(0, ncol = (df.width+2))
    df.new <- as.data.frame(matrix1)
    #print(dim(df.new))
    for(i in 1:df.length){
      i.msg <- paste0("adding categories to row ", i, " of ", df.length)
      #print(i.msg)
      df.i <- df.append[i,]
      #print(df.i)
      #print(head(hh.list[,2]))
      #print(df.append$SCHOOL.NAME[i])
      df.i.cats <- hh.list[hh.list[,2] %in% df.append$SCHOOL.NAME[i],c(1,2,3,4)]
      if(nrow(df.i.cats)==0){
        df.i.cats2 <- rep(0, 2)
      } else if(nrow(df.i.cats)>=2){
        df.i.cats2 <- hh.list[hh.list[,1] %in% df.i.cats[,1],]
        df.i.cats2 <- df.i.cats2[1,]
      } else if(nrow(df.i.cats)==1){
        df.i.cats2 <- df.i.cats
      }
      #print(df.i.cats)
      #print(nrow(df.i.cats))
      #print(dim(df.i.cats))
      #print("cats2 =")
      #print(df.i.cats2)
      
      df.i.append <- c(df.i, df.i.cats2[c(3:4)])
      df.i.df <- as.data.frame(df.i.append)
      
      cnames <- colnames(df.i.df)
      cname.len <- length(cnames)
      
      cnames[c((cname.len - 1),(cname.len))] <- c("Category", "Include.Exclude") # IF DOMS COL ADDED, MAYBE USE cnames[c(41,42)] <- c("Category", "Include.Exclude")
      colnames(df.i.df) <- cnames
      colnames(df.new) <- colnames(df.i.df)
      df.new <- rbind(df.new, df.i.df)
      
    }
    df.new
  }
  
  #END OF hhpart.append.R
  
  cols.owns <- function(object, market.column){
    
    object.width <- length(colnames(object))
    
    mark.own <- read.csv("D://Users/SPritchard/Music/Documents/R/zip-sort/market-ownership-old.csv", stringsAsFactors = FALSE)
    
    object.wgeos <- object
    market.col <- object.width
    
    owners.df <- data.frame("bd" = 0, "crd" = 0, "owner" = 0, "rd" = 0)
    owners.cols <- colnames(owners.df)
    vec.len <- nrow(object.wgeos)
    #print(head(mark.own, 4))
    for(t in 1:vec.len){
      msg.t <- paste0("adding owners to row ", t, " of ", vec.len)
      #print(msg.t)
      owners.t <- if(nrow(mark.own[mark.own[, 4] %in% object.wgeos[t, 4], c(5, 6, 7, 8)])>=1){
        mark.own[mark.own[, 4] %in% object.wgeos[t, 4], c(5, 6, 7, 8)]
      } else {
        data.frame("A"=1, "B"=1, "C"=1, "D"=1)
      }
      owners.t <- owners.t[1,]
      #print(head(mark.own[,4]))
      #print(object.wgeos[t, market.col])
      #print(owners.t)
      colnames(owners.t) <- owners.cols
      owners.df <- rbind(owners.df, owners.t)
      msg2 <- paste("second loop number", t)
      #print(msg2)
    }
    #print("loop 2 complete")
    owners.df <- owners.df[-1,]
    #print(head(object.wgeos))
    #print(tail(object.wgeos))
    #print(head(owners.df))
    #print(tail(owners.df))
    
    obj.geo.own <- cbind(object.wgeos, owners.df)
    #print("do we get this far?")
    obj.wth <- length(colnames(obj.geo.own))
    
    #print("checking split markets")
    ss.evan <- obj.geo.own[(obj.geo.own$CP4.MARKET == "North LA" 
                            | obj.geo.own$CP4.MARKET == "South Shore")
                           | obj.geo.own$CP4.MARKET == "Downers Grove (East)" ,]
    ss.evan.rows <- rownames(ss.evan)
    ss.evan.length <- nrow(ss.evan)
    
    school.table <- read.csv("D://Users/SPritchard/Music/Documents/R/zip-sort/ss.evan.owns.csv", stringsAsFactors = FALSE)
    zip.table <- read.csv("D://Users/SPritchard/Music/Documents/R/zip-sort/zip-to-market.csv", stringsAsFactors = FALSE)
    
    zips <- substr(zip.table[,1], 2, 6)
    zips <- as.numeric(zips)
    zip.table[,1] <- zips
    
    new.owners <- read.csv("D://Users/SPritchard/Music/Documents/R/zip-sort/market-ownership.csv", stringsAsFactors = FALSE)
    
    for(k in 1:ss.evan.length){
      msg.k <- paste0("checking split market zip ", k, " of ", ss.evan.length)
      #print(msg.k)
      ss.evan.k <- ss.evan[rownames(ss.evan) == ss.evan.rows[k],]
      #print(paste("k =", k))
      #print(class(ss.evan.k))
      #print(dim(ss.evan.k))
      #print(head(ss.evan.k))
      #print(ss.evan.k)
      #print(ss.evan.k[21] != "")
      #print(ss.evan.k[21] %in% school.table$SCHOOL.NAME)
      
      #print(nrow(school.table[school.table$SCHOOL.NAME %in% ss.evan.k[21],]))
      if((ss.evan.k[21] != "") & (ss.evan.k[21] %in% school.table$SCHOOL.NAME)){
        obj.geo.own[rownames(obj.geo.own) == ss.evan.rows[k], c((obj.wth - 3):obj.wth)] <- school.table[school.table$SCHOOL.NAME == ss.evan.k[1,21],c(13:16)]
        #print(obj.geo.own[rownames(obj.geo.own) == ss.evan.rows[k],]) 
      } else {
        #print("no school here")
        ss.evan.kzips <- ss.evan.k[1, c(23:26)]
        ss.evan.kzipsclean <- ss.evan.kzips[!is.na(ss.evan.kzips)]
        zip.check <- ss.evan.kzipsclean[1]
        #print(zip.check)
        
        
        zip.check <- as.character(zip.check)
        if(!is.na(zip.check)){
          
          if(nchar(zip.check) <=3){
            zip.check <- paste0("00",zip.check)
          } else if (nchar(zip.check) == 4){
            zip.check <- paste0("0", zip.check)
          }
          
          zip.check <- as.numeric(zip.check)
          #print(zip.check)
          
          #print(head(zip.table, 2))
          
          new.market <-  zip.table[zip.table[,1] == zip.check, 21 ]
          
          new.market <- new.market[1]
          #print(new.market)
          nmarket.owns <- new.owners[new.owners[,4] == new.market, c(5:8)]
          #print(head(nmarket.owns))
          
          obj.geo.own[rownames(obj.geo.own) == ss.evan.rows[k], c((obj.wth - 3):obj.wth)] <- nmarket.owns
        }
      }
    }
    
    obj.geo.own
  }
  
  #END OF cols.owns3.R
  
  cy.fixed <- three.fix(mtd.obj, class.data.obj, st.date.priormnth, end.date.curmnth)
  cy.append1 <- hhpart.append(cy.fixed)
  cy.append2 <- cols.owns(cy.append1)
  
  #DROP FILE IN CACHE
  cached.file.name <- paste0("D://Users/SPritchard/Music/Documents/R/cached/netbob.fix.thru", gsub("-", "", end.date.curmnth),".csv")
  write.csv(cy.append2, cached.file.name, row.names = FALSE)
  
} # using cached file if available
  
  cy.append2
  
}

#END OF mtd.prep.R

schcap.match <- function(cy.obj, py.obj){
  
  cy.allnb <- sum(cy.obj$NETBOB, na.rm = TRUE)
  cy.miss <- cy.obj[cy.obj$SCHOOL.NAME == "",]
  cy.miss.nb <- sum(cy.miss$NETBOB, na.rm = TRUE)
  cy.perc.capt <- (1-cy.miss.nb/cy.allnb)
  
  py.allnb <- sum(py.obj$NETBOB, na.rm = TRUE)
  py.miss <- py.obj[py.obj$SCHOOL.NAME == "",]
  py.miss.nb <- sum(py.miss$NETBOB, na.rm = TRUE)
  py.perc.capt <- (1-py.miss.nb/py.allnb)
  
  py.coef <- cy.perc.capt/py.perc.capt
  
  py.obj.matched <- py.obj
  py.obj.matched$NETBOB <- (py.obj.matched$NETBOB*py.coef)
  
  cypy.matched <- rbind(cy.obj, py.obj.matched)
  cypy.matched
  
}
#END OF schcap.match.R


nb.horiz.bars <- function(fixed.yy){
  product.group <- character()
  yy.len <- nrow(fixed.yy)
  for(i in 1:yy.len){
    prev.i <- if(fixed.yy$PROGRAM[i] %in% "PREMIER"){
      "Premier"
    } else {
      "Classroom/Async"
    } 
    product.group <- c(product.group, prev.i)
  } 
  fixed.pgroup <- cbind(fixed.yy, product.group)
  fixed.pgrouphh <- fixed.pgroup[fixed.pgroup$Include.Exclude %in% "Okay",]
  fixed.agg <- aggregate(NETBOB ~ owner + product.group + TRANSACTION.YEAR, fixed.pgrouphh, sum)
  fixed.agg <- fixed.agg[!(fixed.agg$owner %in% "1"),]
  fixed.agg <- fixed.agg[!(fixed.agg$owner %in% ""),]

  owner.year <- paste(fixed.agg$owner, fixed.agg$TRANSACTION.YEAR)
  fixed.agg <- cbind(fixed.agg, owner.year)
  fixed.agg <- fixed.agg[order(fixed.agg$owner.year),]

  fixed.agg <- arrange(fixed.agg, desc(NETBOB))
  agg.unique <- unique(fixed.agg$owner)

  agg.levels <- levels(fixed.agg$owner)
  
  #print(paste(pages, "pages needed"))
  for(i in 1:1){
    st.owner <- (i-1)*12+1
    end.owner <- (st.owner+11)
    yy.pg <- fixed.agg[fixed.agg$owner %in% agg.unique[st.owner:end.owner],]

    yy.pg <- arrange(yy.pg, desc(TRANSACTION.YEAR), desc(owner.year)) 
    g <- ggplot(data = fixed.agg, aes(owner.year)) 
    g <- g + geom_bar(aes(fill = product.group, weight = NETBOB), position = position_stack(reverse = TRUE)) +
      coord_flip() + theme(legend.position = "top") + ylab("Net BoB") + xlab("BD/CRD")
    print(g)
  }
}

# end of function

yy.periodtodate <- function(full.obj, cy.start.date, cy.end.date = "latest.available"){
  
  # Watch for monthly numbers imported as factors!
  #1 MATCH TIMELINE OF cy.df TO py.df AND JOIN THEM
  
  full.obj.dates <- full.obj[full.obj$TRANSACTION.DATE != "" & full.obj$TRANSACTION.DATE != "0",]
  full.obj.dates$TRANSACTION.DATE <- as.Date(full.obj.dates$TRANSACTION.DATE, "%m/%d/%Y")
  
  cy.start <- as.Date(cy.start.date, "%Y-%m-%d")
  cy.end <- if(cy.end.date == "latest.available"){
    max(full.obj.dates$TRANSACTION.DATE)
  } else {
    as.Date(cy.end.date, "%Y-%m-%d")
  }
  #cy.end <- max(full.obj.dates$TRANSACTION.DATE)
  cy.yysubset <- full.obj.dates[full.obj.dates$TRANSACTION.DATE >= cy.start
                                & full.obj.dates$TRANSACTION.DATE <= cy.end,]
  #print(head(cy.yysubset))
  py.start <- if((cy.start - 365) <= as.Date("2016-02-29", "%Y-%m-%d")){
    cy.start - 366
  } else {
    cy.start - 365
  }
  #py.start <- (cy.start - 365)
  py.end <- if((cy.end - 365) <= as.Date("2016-02-29", "%Y-%m-%d")){
    cy.end - 366
  } else {
    cy.end - 365
  }
  
  #py.end <- (cy.end - 365)
  py.yysubset <- full.obj.dates[full.obj.dates$TRANSACTION.DATE >= py.start 
                                & full.obj.dates$TRANSACTION.DATE <= py.end,]
  #print(head(py.yysubset))
  #print(tail(py.yysubset))
  cy.py.dates <- rbind(cy.yysubset, py.yysubset)
  #cy.py.dates$TRANSACTION.DATE <- as.Date(cy.py.dates$TRANSACTION.DATE)
  cy.py.dates
}

mqy.dates <- function(cy.df){
  
  # Watch for monthly numbers imported as factors!
  
  cy.df.dates <- cy.df[cy.df$TRANSACTION.DATE != "" & cy.df$TRANSACTION.DATE != "0",]
  #print(head(unique(cy.df.dates$TRANSACTION.DATE), 50))
  cy.df.dates$TRANSACTION.DATE <- as.Date(cy.df.dates$TRANSACTION.DATE, "%m/%d/%Y")
  #print("line 7")
  cy.end <- max(cy.df.dates$TRANSACTION.DATE)
  cy.mo.num <- substr(cy.end, 6,7)
  
  #print("line 11")
  month.quarter.df <- data.frame(m = rep(1:12), 
                                 q = c("01", "01", "01", "04", "04", "04", 
                                       "07", "07", "07", "10", "10", "10"))
  month.start <- as.Date(paste0(substr(cy.end, 1, 8),"01"), "%Y-%m-%d")
  numeric.month <- as.numeric(substr(cy.end, 6, 7))
  #print("line 17")
  
  quarter.month <- month.quarter.df[numeric.month, 2]
  quarter.start <- as.Date(paste0(substr(cy.end, 1, 5), quarter.month ,"-01"), "%Y-%m-%d")
  #print("line 21")
  
  year.start <- as.Date(paste0(substr(cy.end, 1, 5), "01-01"), "%Y-%m-%d")
  
  impt.dates <- c(cy.end, month.start, quarter.start, year.start)
}

# END OF mqy.dates.R

ly.ytlastmonth.fix <- read.csv("D://Users/SPritchard/Music/Documents/R/net-bob-scripts/az/ly.ytlastmonth.fix.csv", stringsAsFactors = FALSE)

setwd("D://Users/SPritchard/Downloads/")
class.data <- read.csv("D://Users/SPritchard/Music/Documents/R/net-bob-scripts/PC Class Data.csv", stringsAsFactors = FALSE)
new.mtd <- new.month("PC NetBoB Daily.xls") 
new.mtd.dates <- as.Date(new.mtd$TRANSACTION.DATE, "%m/%d/%Y")
new.mtd.date.max <- max(new.mtd.dates)
new.mtd.fix <- mtd.prep(new.mtd, class.data, "2016-05-01", new.mtd.date.max)
ly.ytd.fix <- rbind(ly.ytlastmonth.fix, new.mtd.fix) #use this obj on every future script

raw.data.file.name <- paste0("D://Users/SPritchard/Downloads/raw.field.report.data", Sys.Date(),".csv")

write.csv(ly.ytd.fix, raw.data.file.name, row.names = FALSE)

period.start.dates <- mqy.dates(ly.ytd.fix) # vector with 4 dates: 
            #1) latest date in data, 2) month start date, quarter start date, year start date

#mtd.yy.fix <- yy.periodtodate(ly.ytd.fix, period.start.dates[2])

#cy <- mtd.yy.fix[mtd.yy.fix$TRANSACTION.YEAR %in% 2017,]
#py <- mtd.yy.fix[mtd.yy.fix$TRANSACTION.YEAR %in% 2016,]


```
### MTD Ranked Performance by Owner by Points
Points system accounts for % and $ growth (% prior year x $ growth / 1000; if negative = % chg)
```{r, echo=FALSE, fig.height=8, fig.width=8, warning=FALSE}

mtd.yy.fix <- yy.periodtodate(ly.ytd.fix, period.start.dates[2]) 

cy <- mtd.yy.fix[mtd.yy.fix$TRANSACTION.YEAR %in% 2017,]
py <- mtd.yy.fix[mtd.yy.fix$TRANSACTION.YEAR %in% 2016,]

setwd("D://Users/SPritchard/Downloads/")

bd.yyperf.table <- function(cy.df2, py.df2, cy.num){
  
  hug.handshake.dates <- function(cy.df, py.df){
    
    # Watch for monthly numbers imported as factors!
    #1 MATCH TIMELINE OF cy.df TO py.df AND JOIN THEM
    
    cy.df.dates <- cy.df[!(cy.df$TRANSACTION.DATE %in% ""),]
    
    cy.df.dates$TRANSACTION.DATE <- as.Date(cy.df.dates$TRANSACTION.DATE, "%m/%d/%Y")
    
    cy.start <- min(cy.df.dates$TRANSACTION.DATE, na.rm = TRUE)
    cy.end <- max(cy.df.dates$TRANSACTION.DATE, na.rm = TRUE)

    py.df.dates <- py.df[!(py.df$TRANSACTION.DATE %in% ""),]
    py.df.dates$TRANSACTION.DATE <- as.Date(py.df.dates$TRANSACTION.DATE, "%m/%d/%Y")
    py.start <- (cy.start - 365)
    py.end <- (cy.end - 365)

    py.yysubset <- py.df.dates[py.df.dates$TRANSACTION.DATE >= py.start 
                               & py.df.dates$TRANSACTION.DATE <= py.end,]

    cy.py.dates <- rbind(cy.df.dates, py.yysubset)

    cy.py.dates
  }
  
  matched.data <- hug.handshake.dates(cy.df2, py.df2)
  matched.datahh <- matched.data[matched.data$Include.Exclude %in% "Okay",]
  matched.datahh <- matched.datahh[!(matched.datahh$owner %in% "1") ,]
  matched.datahh <- matched.datahh[!(matched.datahh$owner %in% "") ,]
  match.agg <- aggregate(NETBOB ~ owner + TRANSACTION.YEAR, matched.datahh, sum)

  match.agg
  uniq.owners <- unique(match.agg$owner)

  uniq.len <- length(uniq.owners)
  yy.df <- data.frame("owner" = 0, "cy" = 0, "py" = 0)
  for(i in 1:uniq.len){
    bd.i <- uniq.owners[i]
    bd.icy <- match.agg[(match.agg$owner %in% bd.i
                         & match.agg$TRANSACTION.YEAR %in% cy.num), c(2:3)]
    py.num <- (as.numeric(cy.num)-1)

    bd.ipy <- match.agg[(match.agg$owner %in% bd.i
                         & match.agg$TRANSACTION.YEAR %in% py.num), c(2:3)]
    if(nrow(bd.icy) == 1 
       & nrow(bd.ipy) == 1){
      #print(paste("if = yes"))
    
    bd.row <- c(bd.i, bd.icy[2], bd.ipy[2])
    bd.row.df <- as.data.frame(bd.row)

    colnames(bd.row.df) <- colnames(yy.df)
    yy.df <- rbind(yy.df, bd.row.df)
    }
  }
  
  yy.df
  
  yy.df <- yy.df[!(yy.df$owner %in% "0"),]
  diff <- yy.df$cy-yy.df$py
  
  perc.diff <- (diff/(yy.df$py+2000)) # nullifes effect of tiny baselines on denominator
  
  pos.pts <- ((diff + sqrt(perc.diff)*1000)/1000) # need to fix the negative to just be based on % without weighting
  neg.pts <- (perc.diff)*100
  pts <- numeric()
  for(i in 1:length(diff)){
    pts.i <- if(perc.diff[i] >= 0){
      pos.pts[i]
    } else if(yy.df$py[i] < 0){
      yy.df$cy[i]/1000 # if prior year negative, then points are cy /1000
    } else              {
      neg.pts[i] # $ chg is negative then points are 1+ % chg (e.g. -10% growth is -10 points)
    }
    pts <- c(pts, pts.i)
  }
  diff <- paste("$",round(diff, 0))
  perc.diff <- paste0(round(perc.diff*100,1),"%")
  pts <- round(pts, 1)

  yy.dfpts <- cbind(yy.df, diff, perc.diff, pts)
  yy.dfpts <- yy.dfpts[order(pts, decreasing = TRUE),]
  #print(yy.dfpts, 15)
  #print("minimum per month is $10k from H+H")
  yy.dfpts
  
    
}

yy.match <- schcap.match(cy, py)

cy2 <- yy.match[yy.match$TRANSACTION.YEAR %in% 2017,]
py2 <- yy.match[yy.match$TRANSACTION.YEAR %in% 2016,]

grid.data <- bd.yyperf.table(cy2, py2, "2017")
  grid.data$cy <- paste("$", round(grid.data$cy,0))
  grid.data$py <- paste("$", round(grid.data$py,0))
colnames(grid.data) <- c("BD/CRD", "Current Year", "Prior Year", "$ Chg", "% Chg", "HH Points")
grid.rows <- seq_len(nrow(grid.data))
mtd.file.name <- paste0("D://Users/SPritchard/Downloads/mtd", Sys.Date(),".csv")
write.csv(grid.data, mtd.file.name, row.names = FALSE)
grid.table(grid.data, rows = grid.rows)

```

###MTD Chart of Adjusted Year over Year Net BoB by Owner
```{r, echo=FALSE, fig.height=10.4, fig.width=8}
mtd.yy.fix <- yy.periodtodate(ly.ytd.fix, period.start.dates[2])

cy <- mtd.yy.fix[mtd.yy.fix$TRANSACTION.YEAR %in% 2017,]
py <- mtd.yy.fix[mtd.yy.fix$TRANSACTION.YEAR %in% 2016,]

yy.match <- schcap.match(cy, py)
mtd <- nb.horiz.bars(yy.match)

#mtd

cy.obj <- cy2
py.obj <- py2
cy.allnb <- sum(cy.obj$NETBOB, na.rm = TRUE)
cy.miss <- cy.obj[cy.obj$SCHOOL.NAME == "",]
cy.miss.nb <- sum(cy.miss$NETBOB, na.rm = TRUE)
cy.perc.capt <- (1-cy.miss.nb/cy.allnb)
  
py.allnb <- sum(py.obj$NETBOB, na.rm = TRUE)
py.miss <- py.obj[py.obj$SCHOOL.NAME == "",]
py.miss.nb <- sum(py.miss$NETBOB, na.rm = TRUE)
py.perc.capt <- (1-py.miss.nb/py.allnb)
  
py.coef <- cy.perc.capt/py.perc.capt
  
py.obj.matched <- py.obj
py.obj.matched$NETBOB <- (py.obj.matched$NETBOB*py.coef)

# SET UP PRINT MESSAGES WITH SCHOOL MATCH DATA
mtd.cy.perc.capt <- cy.perc.capt
mtd.py.perc.capt <- py.perc.capt
#print(paste0("% of CURRENT year Net BoB with school info = ", (round(cy.perc.capt, 3)*100), "%"))
#print(paste0("% of PRIOR year Net BoB with school info = ", (round(py.perc.capt, 3))*100, "%"))
#print(paste("To equalize, multiply prior year numbers by =", round(cy.perc.capt/py.perc.capt, 3)))
#print(paste("Prior year Net BoB multiplied by coefficient.  For example a prior year transaction of", round(head(py.obj$NETBOB, 1),2), "has become", round(head(py.obj.matched$NETBOB, 1),2)))

```

###QTD Ranked Performance by Owner by Points
Points system accounts for % and $ growth (% prior year x $ growth / 1000; if negative = % chg)
```{r, echo=FALSE, fig.height=10.4, fig.width=8, warning=FALSE}

qtd.yy.fix <- yy.periodtodate(ly.ytd.fix, period.start.dates[3])

cy <- qtd.yy.fix[qtd.yy.fix$TRANSACTION.YEAR %in% 2017,]
py <- qtd.yy.fix[qtd.yy.fix$TRANSACTION.YEAR %in% 2016,]

yy.match <- schcap.match(cy, py)

cy2 <- yy.match[yy.match$TRANSACTION.YEAR %in% 2017,]
py2 <- yy.match[yy.match$TRANSACTION.YEAR %in% 2016,]

grid.data <- bd.yyperf.table(cy2, py2, "2017")
  grid.data$cy <- paste("$", round(grid.data$cy,0))
  grid.data$py <- paste("$", round(grid.data$py,0))
colnames(grid.data) <- c("BD/CRD", "Current Year", "Prior Year", "$ Chg", "% Chg", "HH Points")
grid.rows <- seq_len(nrow(grid.data))
qtd.file.name <- paste0("D://Users/SPritchard/Downloads/qtd", Sys.Date(),".csv")
write.csv(grid.data, qtd.file.name, row.names = FALSE)
grid.table(grid.data, rows = grid.rows)
```

### QTD Chart of Adjusted Year over Year Net BoB by Owner
```{r, echo=FALSE, fig.height=10.4, fig.width=8}
# yy.match is now from qtd above

qtd <- nb.horiz.bars(yy.match)

#qtd

cy.obj <- cy2
py.obj <- py2
cy.allnb <- sum(cy.obj$NETBOB, na.rm = TRUE)
cy.miss <- cy.obj[cy.obj$SCHOOL.NAME == "",]
cy.miss.nb <- sum(cy.miss$NETBOB, na.rm = TRUE)
cy.perc.capt <- (1-cy.miss.nb/cy.allnb)
  
py.allnb <- sum(py.obj$NETBOB, na.rm = TRUE)
py.miss <- py.obj[py.obj$SCHOOL.NAME == "",]
py.miss.nb <- sum(py.miss$NETBOB, na.rm = TRUE)
py.perc.capt <- (1-py.miss.nb/py.allnb)
  
py.coef <- cy.perc.capt/py.perc.capt
  
py.obj.matched <- py.obj
py.obj.matched$NETBOB <- (py.obj.matched$NETBOB*py.coef)
  
# SET UP PRINT MESSAGES WITH SCHOOL MATCH DATA

qtd.cy.perc.capt <- cy.perc.capt
qtd.py.perc.capt <- py.perc.capt
#print(paste0("% of CURRENT year Net BoB with school info = ", (round(cy.perc.capt, 3)*100), "%"))
#print(paste0("% of PRIOR year Net BoB with school info = ", (round(py.perc.capt, 3))*100, "%"))
#print(paste("To equalize, multiply prior year numbers by =", round(cy.perc.capt/py.perc.capt, 3)))
#print(paste("Prior year Net BoB multiplied by coefficient.  For example a prior year transaction of", round(head(py.obj$NETBOB, 1),2), "has become", round(head(py.obj.matched$NETBOB, 1),2)))
```

### YTD Ranked Performance by Owner by Points
Points system accounts for % and $ growth (% prior year x $ growth / 1000; if negative = % chg)
```{r, echo=FALSE, fig.height=10.4, fig.width=8, warning=FALSE}
ytd.yy.fix <- yy.periodtodate(ly.ytd.fix, period.start.dates[4])

cy <- ytd.yy.fix[ytd.yy.fix$TRANSACTION.YEAR %in% 2017,]
py <- ytd.yy.fix[ytd.yy.fix$TRANSACTION.YEAR %in% 2016,]

yy.match <- schcap.match(cy, py)

cy2 <- yy.match[yy.match$TRANSACTION.YEAR %in% 2017,]
py2 <- yy.match[yy.match$TRANSACTION.YEAR %in% 2016,]

grid.data <- bd.yyperf.table(cy2, py2, "2017")
  grid.data$cy <- paste("$", round(grid.data$cy,0))
  grid.data$py <- paste("$", round(grid.data$py,0))
colnames(grid.data) <- c("BD/CRD", "Current Year", "Prior Year", "$ Chg", "% Chg", "HH Points")
grid.rows <- seq_len(nrow(grid.data))
ytd.file.name <- paste0("D://Users/SPritchard/Downloads/ytd", Sys.Date(),".csv")
write.csv(grid.data, ytd.file.name, row.names = FALSE)
grid.table(grid.data, rows = grid.rows)
```

### YTD Chart of Adjusted Year over Year Net BoB by Owner

```{r, echo=FALSE, fig.height=10.4, fig.width=8}
# yy.match is now from ytd above

ytd <- nb.horiz.bars(yy.match)

#ytd

cy.obj <- cy2
py.obj <- py2
cy.allnb <- sum(cy.obj$NETBOB, na.rm = TRUE)
cy.miss <- cy.obj[cy.obj$SCHOOL.NAME == "",]
cy.miss.nb <- sum(cy.miss$NETBOB, na.rm = TRUE)
cy.perc.capt <- (1-cy.miss.nb/cy.allnb)
  
py.allnb <- sum(py.obj$NETBOB, na.rm = TRUE)
py.miss <- py.obj[py.obj$SCHOOL.NAME == "",]
py.miss.nb <- sum(py.miss$NETBOB, na.rm = TRUE)
py.perc.capt <- (1-py.miss.nb/py.allnb)
  
py.coef <- cy.perc.capt/py.perc.capt
  
py.obj.matched <- py.obj
py.obj.matched$NETBOB <- (py.obj.matched$NETBOB*py.coef)

# SET UP PRINT MESSAGES WITH SCHOOL MATCH DATA
print("Month To Date School Name Capture Info:")  

print(paste0("% of CURRENT year Net BoB with school info = ", (round(mtd.cy.perc.capt, 3)*100), "% vs." ,(round(mtd.py.perc.capt, 3))*100, "% PRIOR year"))

#print(paste0("% of CURRENT year Net BoB with school info = ", (round(mtd.cy.perc.capt, 3)*100), "%"))
#print(paste0("% of PRIOR year Net BoB with school info = ", (round(mtd.py.perc.capt, 3))*100, "%"))
#print(paste("To equalize, multiply prior year numbers by =", round(mtd.cy.perc.capt/mtd.py.perc.capt, 3)))

print("Quarter To Date School Name Capture Info:")  
print(paste0("% of CURRENT year Net BoB with school info = ", (round(qtd.cy.perc.capt, 3)*100), "% vs." ,(round(qtd.py.perc.capt, 3))*100, "% PRIOR year"))
#print(paste0("% of PRIOR year Net BoB with school info = ", (round(qtd.py.perc.capt, 3))*100, "%"))
#print(paste("To equalize, multiply prior year numbers by =", round(qtd.cy.perc.capt/qtd.py.perc.capt, 3)))

print("Year To Date School Name Capture Info:")  

print(paste0("% of CURRENT year Net BoB with school info = ", (round(cy.perc.capt, 3)*100), "% vs." ,(round(py.perc.capt, 3))*100, "% PRIOR year"))

#print(paste0("% of PRIOR year Net BoB with school info = ", (round(py.perc.capt, 3))*100, "%"))
#print(paste("To equalize, multiply prior year numbers by =", round(cy.perc.capt/py.perc.capt, 3)))
#print(paste("Prior year Net BoB multiplied by coefficient.  For example a prior year transaction of", round(head(py.obj$NETBOB, 1),2), "has become", round(head(py.obj.matched$NETBOB, 1),2)))
#print(unique(yy.match$TRANSACTION.DATE))

print(paste("Data included through", period.start.dates[1]))

print(paste("Report run at", date()))

```